### 2015-06-26 ids-fusion.tex
The Prelude citation, maybe

The most substantial challenge in managing \idses is the information overload
that they can impose.
Much of this overload comes from the high false positive rate.  This rate is
partly due to
inaccurate sensors.
Another problem is the ``base rate fallacy''~\cite{Axelsson:1999:BFI:319709.319710}:
in intrusion detection, as in
other applications where very unlikely events must be detected, even a seemingly
accurate sensor may yield too many false positives.  Axelsson gives the example
of a 99\% accurate test detecting a disease that strikes only 1/10,000
patients.  The probability of having the disease given a positive test result is
only 1\%.
% %% This next bit seem redundant.
%, although the probability of the sensor labeling correctly is 99\%.
{\ids} users regularly either ignore or partially disable them, unable to absorb
massive streams of false alarms:%
%% TODO Restore for QR'15
%``Users attending an 'ABCs of IDS' event at London's City University yesterday
%  said more the 80 per cent of the alerts they received were false, with one
%  citing 60 alerts he had received about non-existent problems that morning at
%  0300''
~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
cards~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem, showing how our earlier system was able to winnow
the 
flow of reports in a small corporate network~\anoncite{goldman:09Scyllarus}.
Data reduction must join building a comprehensive overview
and overcoming false positives and negatives as goals of \ids fusion.
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction%
% Squash citation here; cited in sentence referencing figure.
%~\anoncite{goldman:09Scyllarus}
.}
  \label{fig:workloadReduction}
\end{figure}

@@

\paragraph{Related work.}
%% TODO Restore for QR'15
%SecurityFocus has developed the
%Attack Registry and Intelligence Service~\shortcite[ARIS]{ARIS}.
%Its extractor consolidates {\ids} reports from four different
%{\idses} into XML, and presents them in an incident
%console.  However it makes no attempts to fuse the reports, nor weigh
%evidence for and against them.
%
%% TODO Restore full version for QR'15
STAT and MetaSTAT~\cite{vigna01:designing}
use finite-state models to detect and fuse events,
but do not attempt to judge the plausibility of different
events.
%MetaSTAT is a fusion system built on a set of STAT-based
%{\idses}~\cite{vigna01:designing}.  
%STAT is signature-based, and detects events by matching
%against extended finite-state event models.
%MetaSTAT uses
%finite-state models of across-sensor events to consume events
%from lower-level sensors at a higher level,
%but does not attempt to judge the plausibility of different
%events.
EMERALD/eBayes~\cite{raid2001-pac} fusion is the most similar to our systems.
Their sensors are Bayes net-based, and the correlation approach
allows ``upstream'' sensors to adjust the priors on ``downstream''
sensors.
Its fusion is limited to clustering alerts that meet a
similarity criterion; they do not have models of high-level events like
ours (see below).  To the best of our knowledge, they do not
address the difficult issues of acquiring probability parameters for \ids fusion.
The Prelude IDS's Correlator
%% TODO Restore full version for QR'15
% allows users to analyze reports sent to Prelude 
%from compatible IDSes~\cite{PreludeCor} following user-provided
%rules.  Its function
is closest to
our clustering subsystem, but knowledge resides in stateful 
rules instead of an ontology of attacks. 
%% TODO Restore full version for QR'15
%The Arcsight Enterprise Security Manager~\cite{ArcsightEsm},
%also ties correlated IDS reports to an installation's security goals
%and vulnerability information.

>>>>

The most substantial challenge in managing \idses is the information overload
that they can impose.
Much of this overload comes from the high false positive rate.  This rate is
partly due to
inaccurate sensors.
Another problem is the ``base rate fallacy''~\cite{Axelsson:1999:BFI:319709.319710}:
in intrusion detection, as in
other applications where very unlikely events must be detected, even a seemingly
accurate sensor may yield too many false positives.  Axelsson gives the example
of a 99\% accurate test detecting a disease that strikes only 1/10,000
patients.  
Although the sensor is accurate, 
the probability of having the disease given a positive test result is
only 1\%.
% %% This next bit seem redundant.
%, although the probability of the sensor labeling correctly is 99\%.

Users regularly ignore or disable their {\idses}, unable to absorb
massive streams of false alarms.
%% TODO Restore for QR'15
%``Users attending an 'ABCs of IDS' event at London's City University yesterday
%  said more the 80 per cent of the alerts they received were false, with one
%  citing 60 alerts he had received about non-existent problems that morning at
%  0300''
% ~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
card records~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem. It shows how our earlier system was able to winnow
the 
flow of reports in a small corporate network~\anoncite{goldman:09Scyllarus}.
% Data reduction must join building a comprehensive overview
% and overcoming false positives and negatives as goals of \ids fusion.
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction%
% Squash citation here; cited in sentence referencing figure.
%~\anoncite{goldman:09Scyllarus}
.}
  \label{fig:workloadReduction}
\end{figure}

@@

\paragraph{Related work.}
%% TODO Restore for QR'15
%SecurityFocus has developed the
%Attack Registry and Intelligence Service~\shortcite[ARIS]{ARIS}.
%Its extractor consolidates {\ids} reports from four different
%{\idses} into XML, and presents them in an incident
%console.  However it makes no attempts to fuse the reports, nor weigh
%evidence for and against them.
%
%% TODO Restore full version for QR'15
STAT and MetaSTAT~\cite{vigna01:designing}
use finite-state models to detect and fuse events,
but do not attempt to judge the plausibility of different
events.
%MetaSTAT is a fusion system built on a set of STAT-based
%{\idses}~\cite{vigna01:designing}.  
%STAT is signature-based, and detects events by matching
%against extended finite-state event models.
%MetaSTAT uses
%finite-state models of across-sensor events to consume events
%from lower-level sensors at a higher level,
%but does not attempt to judge the plausibility of different
%events.
EMERALD/eBayes~\cite{raid2001-pac} fusion is the most similar to our systems.
Their sensors are Bayes net-based, and the correlation approach
allows ``upstream'' sensors to adjust the priors on ``downstream''
sensors.
Its fusion is limited to clustering alerts that meet a
similarity criterion; they do not have models of high-level events like
ours (see below).  To the best of our knowledge, they do not
address the difficult issues of acquiring probability parameters for \ids fusion.
The Prelude IDS's Correlator
%% TODO Restore full version for QR'15
% allows users to analyze reports sent to Prelude 
%from compatible IDSes~\cite{PreludeCorNew} following user-provided
%rules.  Its function
is closest to
our clustering subsystem, but its knowledge resides in stateful 
rules instead of an ontology of attacks~\cite{PreludeCorNew}. 
%% TODO Restore full version for QR'15
%The Arcsight Enterprise Security Manager~\cite{ArcsightEsm},
%also ties correlated IDS reports to an installation's security goals
%and vulnerability information.
